Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations

### 2021-03-31 papers/intro_paper/intro_paper.tex
added responses to referee comments
going through gregorio's commetns sec I and II

The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} also provided us with the first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}. The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events. The no-hair conjecture in GR~\cite{Carter:1971zc,Hansen:1974zz} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin. One
consequence of the no-hair conjecture is that the (complex) QNM
frequencies of gravitational radiation emitted by a perturbed isolated
BH are uniquely determined by its mass and spin. Hence
a test of the no-hair conjecture would involve checking for
consistency between estimates of mass and spin of the remnant object
across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}. An inconsistency would either
indicate a non-BH nature of the remnant object, or an incompleteness
of GR as the underlying theory of gravity.

The consistency between the post-merger signal and the least damped QNM was first demonstrated in
Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analyses~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}. This was later extended to include
overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Bhagwat:2019dtm,Forteza:2020hbw,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
a BBH coalescence, but not necessarily a test of the no-hair
conjecture, which requires the measurement of (at least) two QNMs (BH
spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Carullo:2018gah,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd}. The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.  None of these tests have found evidence for non-BH nature of the remnant
object (as described in GR) in LIGO-Virgo BBH observations.

Ground-based detectors, such as LIGO and Virgo, are most sensitive to
stellar-mass BH binaries that merge near the
minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
very little signal-to-noise ratio (SNR) in the
post-merger signal. Most of the tests mentioned above restrict the data to this post-merger signal, which significantly reduces parameter-estimation capabilities. However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}). In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a
free parameter to be estimated directly from the data. Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{PyRING} analysis in Ref.~\cite{Abbott:2020jks}). Uncertainties
in estimates of the ringdown start-time, as well as an overall lack of
SNR in the post-merger signal, given typical sensitivities of
ground-based detectors, result in significant statistical uncertainties
in the measurement of the QNM frequencies. And hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.

An independent approach to BH spectroscopy, based on the full-signal
analysis, was introduced in Ref.~\cite{Brito:2018rfr}
(henceforth referred to as \paperone). Unlike methods that focus only
on the post-merger signal, it employs the
complete inspiral-merger-ringdown
(IMR) waveform to measure the complex QNM
frequencies. This gives access to the full SNR of the signal,
reducing measurement uncertainties. Moreover, the definition of the
ringdown start time is built into the merger-ringdown model and does not need to be
either left as an additional free parameter or fixed using alternate
definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
realistic astrophysical case in which BHs carry spin. Furthermore,
the IMR waveform model used in this paper is more accurate than what employed in \paperone,
because it contains higher-order corrections in PN theory and it was calibrated to a much larger set
of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}. All astrophysical BHs are expected to be spinning,
and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the
source properties.

The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
the GWTC 1/2  events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
our results and discuss future developments.

@@

The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
\begin{subequations}
\begin{eqnarray}
f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\\ 
\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})
\end{eqnarray}
\end{subequations}
We denote such a parameterized waveform model $\pSEOB$~\footnote{This
waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
  m}(t)$ in general also differ from the GR predictions, since
those functions depend on the QNM complex frequencies, as can be seen
from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
soon after merger deviates from the one predicted by GR.

@@

The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$. One then proceeds to use the Bayes theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
%
\begin{equation}
P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
\label{eq:Bayes_theorem}
\end{equation}
%
where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function. The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$. In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$. The likelihood function can consequently be defined as:
%
\begin{equation}
\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
\label{eq:likelihood}
\end{equation}
%
where $\langle . | . \rangle$ is the usual noise-weighted inner product:
%
\begin{equation}
\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
\label{eq:nwip}
\end{equation}
%
The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation. The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector. We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
GW detector at low-frequency. Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}. Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}. For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.

@@

We additionally investigate the effects of erroneously assuming that
an underlying non-GR signal can be well-described by a GR one. We do
this by estimating the parameters of our non-GR signals using the GR
waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
resulting one- and two-dimensional posteriors are shown in the right
panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
GW150914-like (top) and GW190521-like (bottom) signals
respectively. For both signals, we find the $\SEOB$ estimates are
markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
this impact on the estimation of the GR parameters $\bxigr$ by changing the
magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. This gives us 
confidence that the $\pSEOB$ model can accurately measure QNM 
properties without biasing measurements of inspiral quantities, like masses and spins.

>>>>

The first paper on tests of GR by the LIGO Collaboration~\cite{TheLIGOScientific:2016src} also provided us with the first measurement of the dominant damped-oscillation signal in the ringdown stage of a BBH
coalescence, and more recently a similar measurement was made with the high-mass event GW190521~\cite{Abbott:2020tfl,Abbott:2020mjq}. The set of available measurements was greatly expanded in the latest LIGO-Virgo O3a testing GR paper~\cite{Abbott:2020jks} where a comprehensive analysis of the properties of the remnant object, including the ringdown stage, was reported for tens of GW events. The no-hair conjecture in GR~\cite{Israel:1967wq,Hawking:1971vc,Carter:1971zc,Robinson:1975bv,Mazur:1982db} states that an (electrically neutral) astrophysical BH is completely described by two observables: mass and spin. One
consequence of the no-hair conjecture is that the (complex) QNM
frequencies of gravitational radiation emitted by a perturbed isolated
BH are uniquely determined by its mass and spin. Hence
a test of the no-hair conjecture would involve checking for
consistency between estimates of mass and spin of the remnant object
across multiple QNM frequencies~\cite{Dreyer:2003bv,Berti:2005ys}. An inconsistency would either
indicate a non-BH nature of the remnant object, or an incompleteness
of GR as the underlying theory of gravity.

The consistency between the post-merger signal and the least damped QNM was first demonstrated in
Ref.~\cite{TheLIGOScientific:2016src} for GW150914, and confirmed through several independent analyses~\cite{Brito:2018rfr,Carullo:2019flw,Isi:2019aib,CalderonBustillo:2020tjf}. This was later extended to include
overtones in Refs.~\cite{Giesler:2019uxc,Isi:2019aib,Abbott:2020jks}. Consistency of the late-time waveform with a single QNM is a test of the ringdown of
a BBH coalescence, but not necessarily a test of the no-hair
conjecture, which requires the measurement of (at least) two QNMs (BH
spectroscopy), and consistency between them~\cite{Dreyer:2003bv,Carullo:2018sfu,Isi:2019aib,Bhagwat:2019bwv,Cabero:2019zyt,Maselli:2019mjd,Bhagwat:2019dtm,Forteza:2020hbw}. The nature of the remnant object has also been explored through tests of BH thermodynamics, including the Hawking's area
theorem~\cite{Cabero:2017avf,Isi:2020tac}, the Bekenstein-Hod universal bound~\cite{Carullo:2021yxh}, the BH area quantization~\cite{Foit:2016uxn,Laghi:2020rgl}, \rb{the consistency of the merger frequency with predictions from NR simulations~\cite{Carullo:2018gah}} or through search for echos in the post-merger signal~\cite{Nielsen:2018lkf,Tsang:2019zra,Lo:2018sep,Abedi:2018npz,Abedi:2020sgg,Testa:2018bzd}.  None of these tests have found evidence for non-BH nature of the remnant
object (as described in GR) in LIGO-Virgo BBH observations.

Ground-based detectors, such as LIGO and Virgo, are most sensitive to
stellar-mass BH binaries that merge near the
minimum of their sensitivity band ($\sim 100$ Hz). As a consequence, the
remnant object \textit{rings down} at frequencies where the sensitivity is worse, leaving
very little signal-to-noise ratio (SNR) in the
post-merger signal. Most of the tests mentioned above restrict the data to this post-merger signal \rb{which, while being agnostic to deviations in the pre-merger dynamics, significantly} reduces parameter-estimation capabilities. However, added to a lack of SNR is the ambiguity in clearly defining a start time for the ringdown phase (discussed, for example, in Refs.~\cite{Berti:2007fi,Baibhav:2017jhs,Bhagwat:2017tkm}). In some tests~\cite{Carullo:2018gah,Carullo:2019flw}, the ringdown start time has been left as a
free parameter to be estimated directly from the data. Whereas, in other cases, the ringdown start time is predicted from corresponding full-signal parameter-estimation analyses (see \texttt{pyRing} analysis in Ref.~\cite{Abbott:2020jks}). Uncertainties
in estimates of the ringdown start-time, as well as an overall lack of
SNR in the post-merger signal, given typical sensitivities of
ground-based detectors, \rb{can result in significant statistical uncertainties in the measurement of some of the QNM properties. This is especially true for the measurement of the QNM damping times which are, in general, harder to measure from the data}. Hence, one might want to look at alternate methods to measure QNMs using information from as much as the signal as possible.

An independent approach to BH spectroscopy, based on the full-signal
analysis, was introduced in Ref.~\cite{Brito:2018rfr}
(henceforth referred to as \paperone). Unlike methods that focus only
on the post-merger signal, it employs the
complete inspiral-merger-ringdown
(IMR) waveform to measure the complex QNM
frequencies. \rb{This method assumes that GR provides a very good description of the signal up to merger, while being agnostic about the complex QNM frequencies, which allows us to access to the full SNR of the signal and
reduce measurement uncertainties}. Moreover, the definition of the
ringdown start time is built into the merger-ringdown model and does not need to be
either left as an additional free parameter or fixed using alternate
definitions. While \paperone presented the method and tested it for non-spinning BBHs, here we extend the analysis to the more
realistic astrophysical case in which BHs carry spin. Furthermore,
the IMR waveform model used in this paper is more accurate than what employed in \paperone,
because it contains higher-order corrections in PN theory and it was calibrated to a much larger set
of numerical-relativity (NR) waveforms~\cite{Bohe:2016gbl}. All astrophysical BHs are expected to be spinning,
and ignoring effects of spin has been shown to introduce systematic biases in the measurement of the
source properties.

The rest of the paper is organized as follows. Section~\ref{sec:model} describes our parameterized IMR
waveform model. In Sec.~\ref{sec:method}, we define our framework to test GR, notably how we can measure
complex QNM frequencies with our parameterized model within a Bayesian formalism, and validate it using 
several synthetic-signal injection studies in Gaussian noise in Sec.~\ref{sec:results}. Then, in Sec.~\ref{sec:results_lvc},
we apply our method on real GW events in LIGO and Virgo data. In particular, we analyze
the GWTC-2 events and obtain the most stringent constraints on the dominant (complex) QNM frequecies. Finally, in Sec.~\ref{sec:discussion} we provide a summary of
our results and discuss future developments.

@@

The GR quantities $( f_{\ell m 0}^{GR},\tau_{\ell m 0}^{GR})$ are
constructed using the NR--fitting--formula from Refs.~\cite{Taracchini:2013rva,Hofmann:2016yih}, and are functions of the initial masses and spins, $(m_1, m_2, \chi_1, \chi_2)$. Hence,
\begin{subequations}
\begin{eqnarray}
f_{\ell m 0} &=& f_{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,,\\ 
\tau _{\ell m 0} &=& \tau _{\ell m 0}(m_1, m_2, \chi_1, \chi_2, \delta f_{\ell m 0}, \delta \tau_{\ell m 0})\,.
\end{eqnarray}
\end{subequations}
We denote such a parameterized waveform model $\pSEOB$~\footnote{This
waveform model is called {\tt pSEOBNRv4HM} in LAL.}. We note that when leaving $\sigma_{\ell m}$ to vary
freely, the functions $\tilde{A}_{\ell m}(t)$ and $\tilde{\phi}_{\ell
  m}(t)$ in general also differ from the GR predictions, since
those functions depend on the QNM complex frequencies, as can be seen
from the expressions for $c_{i,c}^{\ell m}$ and $d_{1,c}^{\ell m}$ in Eqs.~(\ref{c1}),
(\ref{c2}), and (\ref{d1}). As a consequence, the ringdown signal (amplitude and phase) 
soon after merger deviates from the one predicted by GR.

@@

The parameterized model, $\pSEOB$, described above introduces an additional set of non-GR parameters, $\bxingr = (\delta f_{\ell m 0},\delta \tau_{\ell m 0})$, corresponding to each $(\ell,m)$ QNM present in the GR waveform model $\SEOB$. One then proceeds to use the Bayes' theorem to obtain the \emph{posterior} probability distribution on $\blambda = \{\bxigr, \bxingr\}$, given a hypothesis $\mathcal{H}$:
%
\begin{equation}
P(\blambda | d, \mathcal{H}) = \frac{P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H})}{P(d|\mathcal{H})},
\label{eq:Bayes_theorem}
\end{equation}
%
where $P(\blambda | \mathcal{H})$ is the \emph{prior} probability distribution, and $\mathcal{L}(d | \blambda, \mathcal{H})$ is called the \emph{likelihood} function. The denominator is a normalization constant $P(d|\mathcal{H}) = \int P(\blambda | \mathcal{H}) \, \mathcal{L}(d | \blambda, \mathcal{H}) \, d\blambda$, called the marginal likelihood, or the \emph{evidence} of the hypothesis $\mathcal{H}$. In this case, our hypothesis $\mathcal{H}$ is that the data contains a GW signal that is described by the $\pSEOB$ waveform model $h(\blambda)$  and stationary Gaussian noise described by a power spectral density (PSD) $S_n(f)$. The likelihood function can consequently be defined as:
%
\begin{equation}
\mathcal{L}(d | \blambda, \mathcal{H}) \propto \exp\big[-\frac{1}{2} \langle d - h(\blambda) \, | \, d -h(\blambda) \rangle \big],
\label{eq:likelihood}
\end{equation}
%
where $\langle . | . \rangle$ is the usual noise-weighted inner product:
%
\begin{equation}
\langle A | B \rangle = \int_{f_\mathrm{low}} ^{f_\mathrm{high}} df \frac{\tilde{A}^*(f)\tilde{B}(f) + \tilde{A}(f)\tilde{B}^*(f)}{S_n(f)}.
\label{eq:nwip}
\end{equation}
%
The quantity $\tilde{A}(f)$ denotes the Fourier transform of $A(t)$ and the $^*$ indicates complex conjugation. The limits of integration ${f_\mathrm{low}}$ and ${f_\mathrm{high}}$ define the bandwidth of the sensitivity of the GW detector. We usually assume ${f_\mathrm{high}}$ to be the Nyquist frequency whereas ${f_\mathrm{low}}$ is dictated by the performance of the
GW detector at low-frequency. Here, we follow the choice made in the LIGO-Virgo analysis~\cite{LIGOScientific:2018mvr,Abbott:2020niy}. Owing to the large dimensionality of the parameter set $\blambda$, the posterior distribution $P(\blambda | d, \mathcal{H})$ in Eq.~(\ref{eq:Bayes_theorem}) is computed by stochastically sampling the parameter space using techniques such as Markov-chain Monte Carlo (MCMC)~\cite{Metropolis:1953am,Hastings:1970aa} or Nested Sampling~\cite{Skilling:2006gxv}. For this paper, we use the \verb+LALInference+~\cite{Veitch:2014wba} and \verb+Bilby+ codes~\cite{Ashton:2018jfp,Smith:2019ucc} that provide an implementation of the parallely tempered MCMC and Nested Sampling algorithms respectively, for computing the posterior distributions.

@@

We additionally investigate the effects of erroneously assuming that
an underlying non-GR signal can be well-described by a GR one. We do
this by estimating the parameters of our non-GR signals using the GR
waveform model $\SEOB$ instead of the parameterized $\pSEOB$.  The
resulting one- and two-dimensional posteriors are shown in the right
panels of Fig.~\ref{fig:simulated_signal_nonGR} by purple curves for the
GW150914-like (top) and GW190521-like (bottom) signals
respectively. For both signals, we find the \abhi{2D} $\SEOB$ estimates are
markedly biased with respect to the $\pSEOB$ estimates.  We investigate 
this impact on the estimation of the GR parameters $\bxigr$ by changing the
magnitude of deviation in the non-GR parameters more in Fig.~\ref{fig:gr_ngr_comparison}. We restrict ourselves 
to a GW150914-like event, and for comparison, add a synthetic signal
with $\df{220} = \dtau{220} = 0.5$, or 50 \% deviation, alongside the
10\% non-GR signal and a signal with no deviation (essentially GR)
mentioned above. The left (right) panels show the
posterior probability distributions of the three signals using the GR,
$\SEOB$ (non-GR, $\pSEOB$) waveform model. The first difference we
note is the $\SEOB$ recoveries yield biased estimates when the
underlying signal is non-GR, while the $\pSEOB$ recoveries do
not. Furthermore, as we increase the deviations, while the $\SEOB$
recoveries expectedly get more biased, the $\pSEOB$ measurements are
robust in consistently recovering the injected value. This gives us 
confidence that the $\pSEOB$ model can accurately measure QNM 
properties without biasing measurements of inspiral quantities, like masses and spins.
